---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# EVDS

The goal of EVDS is to create a way to get data from the Central Bank of Rebuplic of Turkey's official data center, [Elektronik Veri Dagıtım Sistemi](https://evds2.tcmb.gov.tr/index.php?). This package allows it's users to get the data for the interest rates, currency exchange rates and etc. EVDS package is a tool which let's users to easily export data from the desired series. It also allows users to pick the dates they want to work with.  

## Installation

You can install EVDS from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("algopoly/EVDS")
```

## Example

This is a basic example of how can someone use the package to make an analysis. In this [document](https://utkuhangenc.github.io/pj/files/Financial_Analysis.html), there is a sample analysis on the relationship between CBRT's monetary policies and the currency exchange rates. 


