---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# EVDS

The goal of EVDS is to create an efficient way to get data from the Central Bank of Rebuplic of Turkey's official data center, [Elektronik Veri Dagitim Sistemi](https://evds2.tcmb.gov.tr/index.php?). EVDS package is a tool which let's users to easily export data from the desired series. It allows users to preview and select the series they want to work with. Users can also input dates that they want to work on. 

## Installation

You can install EVDS from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("algopoly/EVDS")
```

## Example

This is a basic example of how can someone use the package to make an analysis. In this [document](https://utkuhangenc.github.io/pj/files/Financial_Analysis.html), there is a sample analysis on the relationship between CBRT's monetary policies and the currency exchange rates. 


